% A BEGINNER'S CHEAT SHEET TO VIM
% Author: Lance Lafontaine (lancelafontaine.github.io)
% Last Edit: 2015-01-13
%
% DISCLAIMER: This work is licensed under a Creative Commons Attribution-NonCommercial-ShareAlike 3.0 Unported License (http://creativecommons.org/licenses/by-nc-sa/3.0/). The cheatsheet template was adapted from Winston Chang's version found at http://www.stdout.org/~winston/latex/. This cheatsheet is intended for non-commercial use.


\documentclass[10pt,landscape]{article}
\usepackage{multicol}
\usepackage{ifthen}
\usepackage[landscape]{geometry}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt plus 0.5ex}


% This sets page margins to .5 inch if using letter paper, and to 1cm       
% if using A4 paper. (This probably isn't strictly necessary.)              
% If using another size paper, use default 1cm margins.
\ifthenelse{\lengthtest { \paperwidth = 11in}}
	{ \geometry{top=.5in,left=.5in,right=.5in,bottom=.5in} }
	{\ifthenelse{ \lengthtest{ \paperwidth = 297mm}}
		{\geometry{top=1cm,left=1cm,right=1cm,bottom=1cm} }
		{\geometry{top=1cm,left=1cm,right=1cm,bottom=1cm} }
	}
 
% Redefine section commands to use less space 
\makeatletter
\renewcommand{\section}{\@startsection{section}{1}{0mm}%
                                {-1ex plus -.5ex minus -.2ex}%
                                {0.5ex plus .2ex}%x
                                {\normalfont\large\bfseries}}
\renewcommand{\subsection}{\@startsection{subsection}{2}{0mm}%
                                {-1explus -.5ex minus -.2ex}%
                                {0.5ex plus .2ex}%
                                {\normalfont\normalsize\bfseries}}
\renewcommand{\subsubsection}{\@startsection{subsubsection}{3}{0mm}%
                                {-1ex plus -.5ex minus -.2ex}%
                                {1ex plus .2ex}%
                                {\normalfont\small\bfseries}}
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\raggedright
\begin{multicols}{3}

% multicol parameters                                                       
% These lengths are set only within the two main columns                    
\setlength{\columnseprule}{0.25pt}
\setlength{\premulticols}{1pt}
\setlength{\postmulticols}{1pt}
\setlength{\multicolsep}{1pt}
\setlength{\columnsep}{2pt}

\begin{center}
     \Large{\underline{\textbf{Beginner's Vim Cheat Sheet}}} \\
\end{center}

\textbf{Remember: }\textit{These can all be used with a repeater.}

\section{Movement}
\verb!h/j/k/l! \hfill Move left/down/up/right.\\
\verb!Ctrl+d! \hfill Move half-screen down.\\
\verb!Ctrl+u! \hfill Move half-screen up.\\
\verb!Ctrl+f! \hfill Move full screen forward.\\
\verb!Ctrl+b! \hfill Move full screen backward.\\
\verb! !\\
\verb!M! \hfill Bring cursor to middle of screen.\\
\verb!H! \hfill Bring cursor to top of screen.\\
\verb!3H! \hfill Bring cursor to 3 lines from top of screen.\\
\verb!L! \hfill Bring cursor to bottom of screen.\\
\verb!3L! \hfill Bring cursor to 3 lines from bottom of screen.\\
\verb!zt! \hfill Make cursor position top of window.\\
\verb!zz! \hfill Make cursor position middle of window.\\
\verb!zb! \hfill Make cursor position bottom of window.\\
\verb! !\\
\verb!w/b! \hfill Go to next/previous delimiter.\\
\verb!W/B! \hfill Go to next/previous word.\\
\verb! !\\
\verb!$! \hfill Go to end of line.\\
\verb!^! \hfill Go to first letter of a line.\\
\verb!0! \hfill Go to beginning of a line.\\
\verb!gg/G! \hfill Go to beginning/end of the file.\\
\verb!{/}! \hfill Go to beginning/end of paragraph.\\ 
\verb!8gg! and \verb!8G! and \verb!:8! \hfill Go to line 8.\\
\verb! !\\
\verb!fP! \hfill Find next P in the line.\\
\verb!FP! \hfill Find previous P in the line.\\
\verb!tP! \hfill Find delimiter before next P.\\
\verb!TP! \hfill Find delimiter after previous P.\\
\verb! !\\
\verb!ma! \hfill Record a marker in the register "a".\\
\verb!'a! \hfill Move to marker a.\\
\verb!''! \hfill Toggle between marker and previous position.\\
\verb! !\\
\verb!v! \hfill Visual mode. \verb!j/k! to highlight text.\\
\verb!V! \hfill Visual Line mode. Highlight full lines.\\
\verb! !\\
\textit{In Visual mode, pressing \% under a bracket highlights until matching bracket.}\\
\verb! !\\

\section{Editing}

\verb!o/O! \hfill Add line below/above, enter insert mode.\\
\verb! ! \\
\verb!x/X! \hfill Delete character on/before cursor.\\
\verb! !\\
\verb!dw/db! \hfill Delete next/previous word.\\
\verb!cw/cb! \hfill Change next/previous word.\\
\verb! !\\
\verb!dd/cc! \hfill Delete/change entire line.\\
\verb! !\\
\verb!dj/cj! \hfill Delete/change two lines downward.\\\
\verb!dk/ck! \hfill Delete/change two lines upward.\\
\verb! !\\
\verb!d[motion]! \hfill Delete according to motion.\\
\verb!c[motion]! \hfill Change according to motion.\\
\verb! !\\
\verb!di"/ci"! \hfill Delete/change text inside "".\\
\verb!da"/ca"! \hfill Delete/change text inside "", delete "".\\
\verb! ! \\
\verb!u! \hfill Undo change.\\
\verb!Ctrl + r! \hfill Redo change.\\
\verb! !\\
\verb!yw/yy! \hfill Copy a word/line.\\
\verb! ! \\
\verb!p/P! \hfill Paste, delete character on/after cursor.\\
\verb! !\\
\verb!>>/<<! \hfill Indent/unindent in normal mode.\\
\verb!=3j! \hfill Autoindent 3 lines after cursor.\\

\section{Search and Replace}
\verb!/[searchterm]! \hfill Search. \verb!n/N! for next/previous.\\
\verb!?[searchterm]! \hfill Backward search.\\
\textit{You can use regular expressions and escape chars.}\\
\textit{Can be used as motions with delete, change, copy.}\\
\verb! !\\
\verb!:%s:old:new! \hfill Replace old by new. \verb!%! is the scope.\\
\hfill \verb!:! \textit{can be replaced by other separators.}\\
\verb!:%s:old:new:c! \hfill Prompt before each replacement.\\

\section{Macros}
\verb!qa! \hfill Record a macro in register "a".\\
\verb!j0q! \hfill Stop recording the macro.\\
\verb!:reg! \hfill List all registers.\\
\verb!@a! \hfill Execute macro in register "a".\\
\verb!@@! \hfill Execute previous macro.\\

\section{Buffers, Windows and Tabs}
\verb!:ls! \hfill List all buffers in session.\\
\verb!:bn! \hfill Navigate to next buffer.\\
\verb!:bp! or \verb!:b#! \hfill Navigate to previous buffer.\\
\verb!:bf! \hfill Navigate to first buffer.\\
\verb!:bd! \hfill Delete current buffer.\\
\verb!:bd1! \hfill Delete buffer labeled "1".\\ 
\verb! !\\
\verb!:vs ~/file! \hfill Open file in vertical pane.\\
\verb!:sp ~/file! \hfill Open file in horizontal pane.\\   
\verb!:vert sb2! \hfill Open buffer 2 in vertical pane.\\
\verb!:sb2! \hfill Opens buffer 2 in horizontal pane.\\
\verb! !\\
\verb!Ctrl + w + h/j/k/l! \hfill Move to * window.\\
\verb!Ctrl + w + /H/J/K/L! \hfill Move window to * side.\\                                   
\verb!Ctrl + w + 1+! \hfill Increase window height by 1.\\      
\verb!Ctrl + w + 1-! \hfill Decrease window height by 1.\\                                                                        
\verb!Ctrl + w + >!  \hfill Increase window width by 1.\\     
\verb!Ctrl + w + <!  \hfill Decrease window width by 1.\\           
\verb!Ctrl + w + =!  \hfill Equalize height and width of all windows.\\
\verb! !\\
\verb!:e ~/file! \hfill Edit a file.\\
\verb!:tabe ~/file! \hfill Edit file in new tab.\\
\verb!gt! \hfill Move one tab forward.\\
\verb!gT! \hfill Move one tab backward.\\

\section{Miscellaneous}
\verb!:se ft=python! \hfill sets filetype.\\
\verb!:so ~/file! \hfill rebuilds a file.\\
\verb!:so %! \hfill rebuilds this file.\\
\verb!:sav ~/file! \hfill Saves file elsewhere.\\
\verb! !\\
\verb!:!!\verb!ls -lah! \hfill Access the command line.\\
\verb!:r !!\verb!date! \hfill Append command output to cursor.\\
\verb! !\\
\verb!:map ,s :sav<CR>! \hfill Map ",rs" to cmd. CR is Enter.\\

\section{Defined in my .vimrc}

\verb!OO! \hfill Insert line above cursor.\\
\verb!oo! \hfill Insert line below cursor.\\
\verb!,ci! \hfill Toggle line comments.\\
\verb!,n! \hfill Toggle file navigation.\\
\verb!,k! \hfill Strip whitespace.\\

\end{multicols}
\end{document}